Quality Definitions of Qualities

### 2021-10-13 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
fixed typo
added mathematical definition of abstraction comment

\begin{itemize}
  \item Definition \ref{IEEEunambiguity} mentions the ``Software Requirements Specification'' document and, the specifically related term, ``requirement''. We feel that for the sake of abstraction we should not have the definition focus solely on this specific document and its related term, so we do not include these in the chosen definition.
  \item The term ``interpretation'' is found in both Definition \ref{IEEEunambiguity} and Definition \ref{UnambiguitySelected} and is kept in the chosen definition.
  \item The first two part of Definition \ref{UnambiguitySelected} can be succinctly restated as ``having one interpretation''.
  \item The fourth part of Definition \ref{UnambiguitySelected} can be added to the above phrase, resulting in the new phrase ``having one clear interpretation''. This removes the possibility of one vague interpretation, also addressing the third part of Definition \ref{UnambiguitySelected}.
  \item The new phrase ``having one clear interpretation'' is still ambiguous as there could be one clear interpretation, and one or more vague interpretations. This is addressed by adding a phrase stating that there are no other possible interpretations besides the one clear interpretation.
\end{itemize}

@@

>>>>

\begin{itemize}
  \item Definition \ref{IEEEunambiguity} mentions the ``Software Requirements Specification'' document and, the specifically related term, ``requirement''. We feel that for the sake of abstraction we should not have the definition focus solely on this specific document and its related term, so we do not include these in the chosen definition.
  \item The term ``interpretation'' is found in both Definition \ref{IEEEunambiguity} and Definition \ref{UnambiguitySelected} and is kept in the chosen definition.
  \item The first two parts of Definition \ref{UnambiguitySelected} can be succinctly restated as ``having one interpretation''.
  \item The fourth part of Definition \ref{UnambiguitySelected} can be added to the above phrase, resulting in the new phrase ``having one clear interpretation''. This removes the possibility of one vague interpretation, also addressing the third part of Definition \ref{UnambiguitySelected}.
  \item The new phrase ``having one clear interpretation'' is still ambiguous as there could be one clear interpretation, and one or more vague interpretations. This is addressed by adding a phrase stating that there are no other possible interpretations besides the one clear interpretation.
\end{itemize}

@@

We are not exploring a mathematical definition of abstraction at this time. \cite{ma1991types} discuss type-based abstraction captured in mathematical theory.
